Test parsing of Proff.no table

### 2022-07-09 Test parsing of Proff table.Rmd
Added link to Tabula. More visualisations.
More visualisations.

ggplotly(plot)
```

>>>>

plot2 <- Kors |> 
  filter(REGNSKAPSPERIODE == "SUM EGENKAPITAL OG GJELD") |> 
  ggplot(aes(year, value)) +
  geom_col()

ggplotly(plot)
ggplotly(plot2)

Kors |> 
  filter(REGNSKAPSPERIODE == "Driftsresultat") |> 
  ggplot(aes(year, value)) +
  geom_col()

Kors |> 
  filter(REGNSKAPSPERIODE == "Lønn") |> 
  ggplot(aes(year, value)) +
  geom_col()

Kors |> 
  filter(REGNSKAPSPERIODE == "Årsresultat") |> 
  mutate(
    profit = ifelse(value >= 0, TRUE, FALSE)
  ) |> 
  ggplot(aes(year, value * 1000, fill = profit)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "", big.mark = ".",
                                                   decimal.mark = ",")) +
  theme(legend.position = "none", axis.title.y = element_blank())

Kors |> 
  filter(REGNSKAPSPERIODE == "Ordinært resultat") |> 
  mutate(
    profit = ifelse(value >= 0, TRUE, FALSE)
  ) |> 
  ggplot(aes(year, value * 1000, fill = profit)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "", big.mark = ".",
                                                   decimal.mark = ",")) +
  theme(legend.position = "none", axis.title.y = element_blank())

?element
?theme
```
